Storing messages with multipartite neural cliques

### 2014-07-06 Articles/article.tex
correction mesures
peite modif

	 \begin{abstract}
	 	We extend recently introduced associative memories based on clustered cliques to multipartite cliques. We propose a variant of the classic retrieving rule. We study its performance relatively to the former one for retrieving partially erased and corrupted messages. We provide both analytical and simulation results showing improvements in networks capacities.
	 \end{abstract}

@@

		\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure4g1}
		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
	\end{figure}

@@

	\newpage
	$\,$
	\newpage
	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/1comppsic4l512g1}
		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
	\end{figure}

>>>>

	 \begin{abstract}
	 	We extend recently introduced associative memories based on clustered cliques to multipartite cliques. We propose a variant of the classic retrieving rule. We study its performance relatively to the former one for retrieving partially erased or corrupted messages. We provide both analytical and simulation results showing improvements in both networks capacities and resilience.
	 \end{abstract}

@@

		\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/5portant_erasures_c8l256}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
	\end{figure}

@@

	\newpage
	$\,$
	\newpage
	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/4portant_psi_c8l256e4}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks}
	\end{figure}
